bad forecast good decision

### 2020-07-08 notebook/bad-forecast-good-decision.Rmd
exploring more

```{r}
states <- seq(0,20, length.out = 200)
actions <- states
obs <- states
sigma_g <- 0.04
reward_fn <- function(x,h) pmin(x,h)
discount <- 0.99

# K is at twice max of f3; 8 * K_3 / 5
f1 <- function(x, h = 0, r = 2, K = 10 * 8 / 5){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
}
f2 <- function(x, h = 0, r = 1, K = 10){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
}

@@

transitions <- lapply(models, function(f) transition_matrices(f, states, actions, sigma_g))

@@

Note that the pattern is not driven merely be differences in the unfished equilibrium.  Compare forecast performance under management.  Score is the sum of the log probabilities of observed outcomes, given the

```{r}
scores <- sims %>%
  mutate(next_state = dplyr::lead(state_index), model = as.integer(model)) %>%
  filter(model < 3) %>%
  select(time, state_index, next_state, action_index, model, reps) %>% 
  rowwise() %>%
  mutate(prob =  transitions[[model]][state_index, next_state, action_index] ) %>% 
  group_by(reps, model) %>%
  summarise(score = sum(log(prob)))

scores %>% group_by(model) %>% summarise(mean_score = mean(score))

>>>>

```{r}
states <- seq(0,25, length.out = 200)
actions <- states
obs <- states
sigma_g <- 0.05
reward_fn <- function(x,h) pmin(x,h)
discount <- 0.99

# K is at twice max of f3; 8 * K_3 / 5
f1 <- function(x, h = 0, r = 2, K = 10 * 8 / 5){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
}
f2 <- function(x, h = 0, r = 0.5, K = 10){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
}

@@

model_sigmas <- c(sigma_g, sigma_g, sigma_g)
transitions <- lapply(seq_along(models), function(i) transition_matrices(models[[i]], states, actions, model_sigmas[[i]]))

@@

```{r}
compare <- sims %>%
  mutate(next_state = dplyr::lead(state_index), model = as.integer(model)) %>%
  filter(reps == 2, time < 10) %>%
  rowwise() %>%
  mutate(prob =  transitions[[model]][state_index, next_state, action_index],
         expected = transitions[[model]][state_index, , action_index]  %*% states,
         low = states[ max(which(cumsum(transitions[[model]][state_index,,action_index]) < 0.025)) ],
         high = states[ min(which(cumsum(transitions[[model]][state_index,,action_index]) > 0.975)) ],
         true = states[ next_state],
         model = as.character(model))

compare %>% filter(model < 3) %>% 
  select(time, model, true, expected, low, high) %>% 
  ggplot(aes(time, col = model, fill = model)) + 
  geom_point(aes(y = true), pch = "*", size = 10) +
  geom_point(aes(y = expected)) + 
  geom_errorbar(aes(ymin = low, ymax = high), alpha = 0.5)
```

```{r}
scores <- sims %>%
  mutate(next_state = dplyr::lead(state_index), model = as.integer(model)) %>%
  filter(model < 3) %>%
  select(time, state_index, next_state, action_index, model, reps) %>% 
  rowwise() %>%
  mutate(prob =  transitions[[model]][state_index, next_state, action_index] ) %>% 
  group_by(reps, model) %>%
  summarise(score = sum(log(prob))) 
```

````{r}
scores %>% group_by(model) %>% summarise(mean_score = mean(score))
